\section{Introduction}
Automatic image colorization consists in automatically assigning colors to greyscale images, in a plausible and
realistic way, that could potentially fool a human observer. This task is particularly important for advertisement
and film industries, but also in photography and in artist assistance \cite{chromagan}.
In fact, as Yoo et al. underlined in \cite{animation}, "coloring images is one of the most laborious and expensive
stages when making modern day animation movies and comics. Automating the colorization process can help to reduce
both cost and time required in producing comics or animated movies."

Despite many advances in deep learning, automatic image colorization is still nowadays considered a difficult task
and its applications are still limited. This is mainly due to the fact that image colorization is an ill-posed
problem that doesn't have a unique solution \cite{su} \cite{chromagan}. Indeed, from a mathematical point of view,
it requires to map a 2D greyscale image to a 3D colored one, and there are multiple plausible solutions that can
be effectively used to colorize the same object.

In our project we want to explore some of the most recent models for automatic image colorization, such as
Eccv16 \cite{zhang}, Siggraph17 \cite{siggraph}, ChromaGAN \cite{chromagan}, InstColorization \cite{su}.
We also used an older model developed by Dahl \cite{dahl} and we implemented a simple model based on a
convolutional autoencoder, as a baseline.
To compare all these models, we performed the classification task on the colorized images and measured the
classification accuracy. Furthermore, we computed some advanced metrics, such as Learned Perceptual Image Patch
Similarity (LPIPS), Peak Signal-to-Noise Ratio (PSNR) and Structural Similarity (SSIM) and performed a short
Turing Test.

Overall, the best performing models for what concerns the quantitative metrics are the most recent ones,
i.e. ChromaGAN and InstColorization, as we expected. However, in the Turing Test the best performing models
are ChromaGAN and Siggraph17, while InstColorization performed poorly.



% existing colorization models ignore rare instances present in data and opt to learn the most frequent colors
% to generalize over the data.
% Existing colorization models suffer from the dominant color effect, illustrated in Fig. 2. This effect occurs when
% a colorization model only learns to color with a few dominant colors present in the training set.
% Figure 2. Dominant color effect commonly encountered by deep colorization models. Deep colorization models tend
% to ignore diverse colors present in a training set and opt to learn only a few dominant colors. Using the most
% dominant color can be effective in minimizing the overall loss but yields unsatisfactory re- sults. One can see
% that the outputs of [34] are dominated by the most prevalent color (red).

