\documentclass[10pt,twocolumn,letterpaper]{article}

\usepackage{cvpr}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\graphicspath{./img}
\usepackage{amsmath}
\usepackage{amssymb,bbm,xcolor}
\usepackage[breaklinks=true,bookmarks=false]{hyperref}
\usepackage{lipsum}
\usepackage{listings}
\usepackage{mathtools,eucal}
\usepackage{graphicx}

\usepackage{bbold}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\usepackage{booktabs, multicol, xcolor}
\usepackage[shortlabels]{enumitem}
\usepackage{changepage}
\cvprfinalcopy % *** Uncomment this line for the final submission
\setcounter{page}{1}
\renewcommand{\figurename}{Figure}
\usepackage{amsmath}
\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator*{\argmin}{arg\,min}
\DeclareMathAlphabet\mathbfcal{OMS}{cmsy}{b}{n}
\usepackage[T1]{fontenc}
\usepackage{flushend}

% Include other packages here, before hyperref.

% If you comment hyperref and then uncomment it, you should delete
% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
% run, let it finish, and you should be clear).
\usepackage[breaklinks=true,bookmarks=false]{hyperref}

\cvprfinalcopy % *** Uncomment this line for the final submission

% Pages are numbered in submission mode, and unnumbered in camera-ready
%\ifcvprfinal\pagestyle{empty}\fi
\setcounter{page}{1}

\begin{document}
\title{Automatic image colorization: a comparative overview}
\author{Bigarella Chiara\\
{\tt\small Student nr. 2004248}
% For a paper whose authors are all at the same institution,
% omit the following lines up until the closing ``}''.
% Additional authors and addresses can be added with ``\and'',
% just like the second author.
% To save space, use either the email address or home page, not both
\and
Poletti Silvia\\
{\tt\small Student nr. 1239133}
}

\maketitle
%\thispagestyle{empty}

%%%%%%%%% ABSTRACT
\begin{abstract}
   The ABSTRACT is to be in fully-justified italicized text, at the top
   of the left-hand column, below the author and affiliation
   information. Use the word ``Abstract'' as the title, in 12-point
   Times, boldface type, centered relative to the column, initially
   capitalized. The abstract is to be in 10-point, single-spaced type.
   Leave two blank lines after the Abstract, then begin the main text.
   Abstract should be no longer than 300 words.
\end{abstract}

\input{intro}
\input{related-work}
\input{dataset}

\section{Methods}
In order to carry out a comparative overview about automatic image colorization, we built, trained and tested a simple autoencoder based on cartoonization, to be considered as baseline. Then, we tested some state-of-the-art pre-trained models taken from the literature: Dahl, Zhang and its upgraded version Siggraph, ChromaGAN and InstColorization.

\input{baseline}
\input{dahl}
\input{zhang}
\input{chromagan}
\input{su}

\section{Experiments}
To compare the results of each model, we computed several metrics: classification with AlexNet, LPIPS, PSNR and SSIM (all quantitative metrics) and a Turing test on few images (qualitative metric). Finally, we applied image filtering to evaluate possible improvements in the performances.

\input{classification}
\input{metrics}
\input{turing}
\input{filter}

\input{conclusion}

{\small
\bibliographystyle{ieee_fullname}
\bibliography{egbib}
}

\end{document}
